Ripple Consensus Review

### 2015-05-05 paper.tex
Typo's
Thanks Tim Swanson!

Unlike Bitcoin, transactions increment and decrement account balances; they do
not directly consume the output of other transactions. To prevent replay
attacks accounts and transaction have sequence numbers; a transaction is only
valid if the Sequence number is exactly one greater than the last-valided
transaction from the same account. Additionally an optional AccountTxnID field
is available for use within transactions; the transaction is only valid if the
sending account's previously-sent transaction matches the provided hash.

@@

The actual process of determining what version of the ledger is correct starts
with the Unique Node Listi, (UNL) a list of public keys meant to be associated
with active nodes the node operator believes are
``unique''.\cite{ripple-wiki-unl} Ripple Labs suggests that UNL's ``should have
100+ nodes on them.''\cite{ripple-wiki-unl} and provides a ``starter'' UNL at
\url{https://ripple.com/ripple.txt} with $5$ to $8$ nodes.\footnote{Exactly how this UNL is
generated is unknown; the author downloaded it on multiple occasions getting
between $5$ to $8$ nodes each time, mostly the same.}

@@

What's actually happened is Russian cyberwarfare experts created a fake
consensus uses stolen Swiss and French private keys. Russia of course
officially signed this fake consensus, as well as the real consensus, taking
the position this was an above-the-board court ordered operation; China also
signed, but doesn't officially say why. The wealthy Chinese investor
conveniently claims to have suddenly found out about the ``fake'' oil importer
and on the real Ripple ledger has the funds frozen by the Chinese bank backing
them - not a big deal with the money still sitting in the original account he
deposited it too, still under Chinese jurisdiction.

>>>>

Unlike Bitcoin, transactions increment and decrement account balances; they do
not directly consume the output of other transactions. To prevent replay
attacks, accounts and transactions have sequence numbers; a transaction is only
valid if the Sequence number is exactly one greater than the last-valided
transaction from the same account. Additionally an optional AccountTxnID field
is available for use within transactions; the transaction is only valid if the
sending account's previously-sent transaction matches the provided hash.

@@

The actual process of determining what version of the ledger is correct starts
with the Unique Node List, (UNL) a list of public keys meant to be associated
with active nodes the node operator believes are
``unique''.\cite{ripple-wiki-unl} Ripple Labs suggests that UNL's ``should have
100+ nodes on them.''\cite{ripple-wiki-unl} and provides a ``starter'' UNL at
\url{https://ripple.com/ripple.txt} with $5$ to $8$ nodes.\footnote{Exactly how this UNL is
generated is unknown; the author downloaded it on multiple occasions getting
between $5$ to $8$ nodes each time, mostly the same.}

@@

What's actually happened is Russian cyberwarfare experts created a fake
consensus using stolen Swiss and French private keys. Russia of course
officially signed this fake consensus, as well as the real consensus, taking
the position this was an above-the-board court ordered operation; China also
signed, but doesn't officially say why. The wealthy Chinese investor
conveniently claims to have suddenly found out about the ``fake'' oil importer
and on the real Ripple ledger has the funds frozen by the Chinese bank backing
them - not a big deal with the money still sitting in the original account he
deposited it too, still under Chinese jurisdiction.
